Template for preparing your research report submission to PNAS using RMarkdown

### 2020-07-16 Manuscript/pnas_article-Template/skeleton/skeleton.tex

\title{A Standardized Effect Size for Evaluating and Comparing the Strength of
Phylogenetic Signal}

\author[a]{Dean C. Adams}
\author[a,b]{Erica K. Baken}
\author[b]{Michael L. Collyer}

  \affil[a]{Department of Ecology, Evolution, and Organismal Biology, Iowa State
University, Ames, Iowa, USA.}
  \affil[b]{Department of Science, Chatham University, Pittsburgh, Pennsylvania,
USA.}

% Please give the surname of the lead author for the running footer
\leadauthor{Adams et al.}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Evolutionary biologists wish to quantify and compare the strength of
phylogenetic signal across traits, but analytical tools for these
comparisons are generally lacking. Here we develop a standardized effect
size based on \(\kappa\) (\(Z_\kappa\)), which measures the strength of
phylogenetic signal on a common statistical scale, and provides a
mechanism for formally comparing the strength of phylogenetic signal
across datasets. Additionally, we find that a commonly used parameter
(Pagel's \(\lambda\)) is insuitable for this purpose. Our procedure
enables biologists to quantitatively address hypotheses that compare the
strength of phylogenetic signal between various phenotypic traits, even
when those traits are found in different evolutionary lineages or have
different units or scales.}

\authorcontributions{D.C.A. designed the research; D.C.A., E.K.B., and M.L.C. performed the
research and wrote the paper.}

\authordeclaration{The authors declare no conflict of interest.}

@@

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
 \keywords{  phylogenetic signal |  macroevolution |  lambda |  kappa  }

\begin{abstract}
Macroevolutionary studies frequently characterize the phylogenetic
signal in phenotypes, and wish to compare the strength of that signal
across traits. However, analytical tools for such comparisons have
largely remained underdeveloped. Here we evaluate the efficacy of one
commonly used parameter (Pagel's \(\lambda\)) to estimate the strength
of phylogenetic signal in phenotypic traits, and evaluate the degree to
which \(\lambda\) correctly identifies known levels of phylogenetic
signal. We find that \(\lambda\) behaves as a Bernoulli random variable,
and that estimates are increasingly skewed at larger and smaller input
levels of phylogenetic signal. Further, the precision of \(\lambda\) in
estimating actual levels of phylogenetic signal is often inaccurate, and
biological interpretations of the strength of phylogenetic signal based
on \(\lambda\) are therefore compromised. We propose a standardized
effect size based on \(\kappa\), (\(Z_\kappa\)), which measures the
strength of phylogenetic signal more reliably than does \(\lambda\), and
places that signal on a common scale for statistical comparison. We
develop tests based on \(Z_\kappa\) to provide a mechanism for formally
comparing the strength of phylogenetic signal across datasets, in much
the same manner as effect sizes may be used to summarize patterns in
quantitative meta-analysis. Our approach extends the phylogenetic
comparative toolkit to address hypotheses that compare the strength of
phylogenetic signal between various phenotypic traits, even when those
traits are found in different evolutionary lineages or have different
units or scales.
\end{abstract}

@@

\acknow{We thank E. Glynne and B. Juarez for comments on early drafts of the
manuscript. This work was supported in part by NSF grant DBI-1902511 (to
D.C.A.) and DBI-1902694 (to M.L.C.).}

@@

References should be cited in numerical order as they appear in text;
this will be done automatically via bibtex, e.g.~All references,
including for the SI, should be included in the main manuscript file.
References appearing in both sections should not be duplicated. SI
references included in tables should be included with the main reference
section.

@@

>>>>

\title{Template for preparing your research report submission to PNAS using
RMarkdown}

\author[a,1,2]{Alice Anonymous}
\author[a,b]{Bob Security}

  \affil[a]{Some Institute of Technology, Department, Street, City, State, Zip}
  \affil[b]{Another University Department, Street, City, State, Zip}

% Please give the surname of the lead author for the running footer
\leadauthor{Anonymous}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement about the significance
of their research paper written at a level understandable to an
undergraduate educated scientist outside their field of speciality. The
primary goal of the Significance Statement is to explain the relevance
of the work in broad context to a broad readership. The Significance
Statement appears in the paper itself and is required for all research
papers.}

\authorcontributions{Please provide details of author contributions here.}

\authordeclaration{Please declare any conflict of interest here.}

\equalauthors{\textsuperscript{} }

@@

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
 \keywords{  one |  two |  optional |  optional |  optional  }

\begin{abstract}
Please provide an abstract of no more than 250 words in a single
paragraph. Abstracts should explain to the general reader the major
contributions of the article. References in the abstract must be cited
in full within the abstract itself and cited in the text.
\end{abstract}

@@

\acknow{Please include your acknowledgments here, set in a single paragraph.
Please do not include any acknowledgments in the Supporting Information,
or anywhere else in the manuscript.}

@@

References should be cited in numerical order as they appear in text;
this will be done automatically via bibtex, e.g.~(1) and (2, 3). All
references, including for the SI, should be included in the main
manuscript file. References appearing in both sections should not be
duplicated. SI references included in tables should be included with the
main reference section.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-belkin2002using}{}%
1. Belkin M, Niyogi P (2002) Using manifold stucture for partially
labeled classification. \emph{Advances in Neural Information Processing
Systems}, pp 929--936.

\leavevmode\hypertarget{ref-berard1994embedding}{}%
2. Bérard P, Besson G, Gallot S (1994) Embedding riemannian manifolds by
their heat kernel. \emph{Geometric \& Functional Analysis GAFA}
4(4):373--398.

\leavevmode\hypertarget{ref-coifman2005geometric}{}%
3. Coifman RR, et al. (2005) Geometric diffusions as a tool for harmonic
analysis and structure definition of data: Diffusion maps.
\emph{Proceedings of the National Academy of Sciences of the United
States of America} 102(21):7426--7431.
